The effect of habitat choice on evolutionary rescue in subdivided populations

### 2020-07-08 ms/revision.tex
fin premiere grosse revision main text

We followed the suggestion and added a sentence explaining this relationship (line~\ref{R1-33}).

\begin{referee}
Fig3:\addnb{R1_34} Please give equation numbers for predictions (goes for all figures).
\end{referee}

@@

However, \florence{we do not provide this formula in the manuscript, because the manuscript is already long.}\st{ since we do not want to go into more details of soft selective sweeps (also due to the length of the manuscript), we do not provide this formula in the manuscript.}

>>>>

We followed the suggestion and added a sentence explaining this relationship (line~\ref{R1-33}).
\florence{(FD Not exactly true for Nnew)}
\begin{referee}
Fig3:\addnb{R1_34} Please give equation numbers for predictions (goes for all figures).
\end{referee}

@@

However, \florence{we do not provide this formula in the manuscript, because the manuscript is already long.}\st{ since we do not want to go into more details of soft selective sweeps (also due to the length of the manuscript), we do not provide this formula in the manuscript.} \florence{not soft sweep}
